<!--
  %\VignetteEngine{knitr}
  %\VignetteIndexEntry{Setting Up Accounts}
-->

```{r twitteR}
library(twitteR)
```

Set up a `twitter` app at https://dev.twitter.com/apps

Fill in all the pertinent information.

To get OAuth tokens, go to `Test OAuth`, and it will show you the `consumer key` and `consumer secret`. I stored these in a folder that is not part of the package, in `keys/tokent.txt` and `keys/secret.txt`, respectively.

```{r handshake, eval=FALSE}
requestURL <- "https://api.twitter.com/oauth/request_token"
accessURL <- "https://api.twitter.com/oauth/access_token"
authURL <- "https://api.twitter.com/oauth/authorize"

token <- scan("keys/twitterToken.txt", what="character", n=1)
secret <- scan("keys/twitterSecret.txt", what="character", n=1)

twitterCredentials <- OAuthFactory$new(consumerKey=token,
                                       consumerSecret=secret,
                                       requestURL=requestURL,
                                       accessURL=accessURL,
                                       authURL=authURL)

twitterCredentials$handshake()
registerTwitterOAuth(twitterCredentials)

testTweets <- homeTimeline()

save(twitterCredentials, file="keys/twitteRCredentials.RData") # saves for further use
```

Note that we have saved the credentials to a file that again is not part of the package. If we want to use our credentials later, we simply re-load them.

```{r reload, eval=FALSE}
load("keys/twitteRCredentials.RData")
registerTwitterOAuth(twitterCredentials)
testTweets <- homeTimeline()
```

