<!--
  %\VignetteEngine{knitr}
  %\VignetteIndexEntry{Setting Up Accounts}
-->

# Twitter

```{r twitteR}
library(twitteR)
```

Set up a `twitter` app at https://dev.twitter.com/apps

Fill in all the pertinent information.

To get OAuth tokens, go to `Test OAuth`, and it will show you the `consumer key` and `consumer secret`. I stored these in a folder that is not part of the package, in `keys/tokent.txt` and `keys/secret.txt`, respectively.

```{r handshake, eval=FALSE}
requestURL <- "https://api.twitter.com/oauth/request_token"
accessURL <- "https://api.twitter.com/oauth/access_token"
authURL <- "https://api.twitter.com/oauth/authorize"

token <- scan("keys/twitterToken.txt", what="character", n=1)
secret <- scan("keys/twitterSecret.txt", what="character", n=1)

twitterCredentials <- OAuthFactory$new(consumerKey=token,
                                       consumerSecret=secret,
                                       requestURL=requestURL,
                                       accessURL=accessURL,
                                       authURL=authURL)

twitterCredentials$handshake()
registerTwitterOAuth(twitterCredentials)

testTweets <- homeTimeline()

save(twitterCredentials, file="keys/twitteRCredentials.RData") # saves for further use
```

Note that we have saved the credentials to a file that again is not part of the package. If we want to use our credentials later, we simply re-load them.

```{r reload, eval=FALSE}
load("keys/twitteRCredentials.RData")
registerTwitterOAuth(twitterCredentials)
testTweets <- homeTimeline()
```

# Facebook

Set up a Facebook app at https://developers.facebook.com/apps. Fill in the information. 

Again, I have the ID and secret in text files that are not part of the package. During authorization, you will need to go into your Facebook app, 

```{r installSetup, eval=FALSE}
install.packages("Rfacebook")
install.packages("Rook")
library(Rfacebook)
appID <- scan("keys/facebookID.txt", what="character", n=1)
appSecret <- scan("keys/facebookSecret.txt", what="character", n=1)
```

Under `Settings` -> `Basic` -> `Add Platform`, select `Website`, and put in the web address that was supplied above (mine was http://localhost:1410/), and hit enter to continue.

```{r authorizeFacebook, eval=FALSE}
fbAuth <- fbOAuth(app_id=appID, app_secret=appSecret)
save(fbAuth, file="keys/facebookCredentials.RData")
```

```{r checkLoading, eval=FALSE}
load("keys/facebookCredentials.RData")
me <- getUsers("me", token=fbAuth)
me
news <- getNewsfeed(fbAuth)
```

